SMT-Boosted Security Types for Low-Level MPC

### 2025-11-21 toplas26/examples.tex
checkpoint

@@

To evaluate our system especially regarding performance, using the
Satisfiability Modulo Fields theory in cvc5 on an Apple M1 processor,
we have verified correctness of these arithmetic gate libraries and
circuit in fields up to size $\fieldp{2^{31} - 1}$ (an approximation
of 32-bit integers) which takes $\sim$7ms to compute for 3 parties and
not significantly more than for, e.g., $\fieldp{2}$. We have also
verified the semi-homomorphic encryption properties leveraged in the
BDOZ circuit library functions in fields up to size $\fieldp{2^{31} -
  1}$ which take $\sim$8ms for the property used for the postcondition
of the $\ttt{mult}$ gate. This is categorically better performance
than can be achieved using previous brute-force methods in
$\fieldp{2}$ \cite{skalka-near-ppdp24}.

>>>>

\preludetestfig

\paragraph{Implementation and Evaluation}
We have implemented the $\metaprot$ language and automated Hoare logic
using an Antlr parser and Scala backend with cvc5 Java bindings for
interaction with the Satisfiability Modulo Fields theory.  To evaluate
performance, we have written and verified gate libraries and small
circuits using the GMW protocol for binary circuits as excerpted in
Figure \ref{fig-gmwprepost} in Section \ref{section-metalang}, and for
passive and malicious secure arithmetic circuits using Beaver Triple
multiplication as presented in Figures \ref{fig-beaver} and
\ref{fig-beaver-bdoz} in this Section.  We have considered field sizes
typically used to encode binary, 16 bit, 32 bit, and 64 bit
integers. Results are presented in Figure \ref{fig-preludetest}. In
summary, verification is efficient, largely due to the performance of
underlying cvc5 verification. It is categorically better performance
than can be achieved using previous brute-force methods developed in
$\fieldp{2}$ \cite{skalka-near-ppdp24}.

@@
